---
title: "matches today"
---


```{r echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
opts_chunk$set(message = FALSE,
               warning = FALSE)

library(servevolleyR)
library(dplyr)
library(DT)

todays_matches <- readRDS("data/match_stats.RDS")
todays_matches <- todays_matches %>%
    filter(date == Sys.Date())

ind <- sample(x = 1:nrow(todays_matches), size = 2)
```

Where available this page will document a couple of randomly selected games scheduled to play today, `r Sys.Date()`.  Using the data returned by the various scripts found in the repo [here](https://github.com/durtal/talks/tree/gh-pages/traders-conference/example/R), and walked through in the other pages on this site.  There are **`r nrow(todays_matches)`** scheduled:


### `r todays_matches$playerA[ind[1]]` vs `r todays_matches$playerB[ind[1]]`

<div class="row">
<div class="col-sm-6">

Player A, **`r todays_matches$playerA[ind[1]]`** wins **`r todays_matches$pA[ind[1]] * 100`** % of his first serve points, **`r todays_matches$p2A[ind[1]] * 100`**% of his second serve points, and his first serve in is **`r todays_matches$firstServeA[ind[1]] * 100`**%.

Player B, **`r todays_matches$playerB[ind[1]]`** wins **`r todays_matches$pB[ind[1]] * 100`** % of his first serve points, **`r todays_matches$p2B[ind[1]] * 100`**% of his second serve points, and his first serve in is **`r todays_matches$firstServeB[ind[1]] * 100`**%.

```{r}
match_data <- simMatches(n = 1000,
     pA = todays_matches$pA[ind[1]],
     p2A = todays_matches$p2A[ind[1]],
     firstServeA = todays_matches$firstServeA[ind[1]],
     pB = todays_matches$pB[ind[1]],
     p2B = todays_matches$p2B[ind[1]],
     firstServeB = todays_matches$firstServeB[ind[1]],
     sets = 3,
     players = c(todays_matches$playerA[ind[1]],
                 todays_matches$playerB[ind[1]]))
```

</div>
<div class="col-sm-6">

```{r echo=FALSE}
plot(match_data)

objname <- paste0(c(todays_matches$playerA[ind[1]], todays_matches$playerB[ind[1]]), collapse = "_vs_")
objname <- paste0("data/", gsub(" ", "-", objname), "_", Sys.Date(), ".RDS")
saveRDS(match_data, objname)
```
</div>
</div>

<hr>

### `r todays_matches$playerA[ind[2]]` vs `r todays_matches$playerB[ind[2]]`

<div class="row">
<div class="col-sm-6">

Player A, **`r todays_matches$playerA[ind[2]]`** wins **`r todays_matches$pA[ind[2]] * 100`** % of his first serve points, **`r todays_matches$p2A[ind[2]] * 100`**% of his second serve points, and his first serve in is **`r todays_matches$firstServeA[ind[2]] * 100`**%.

Player B, **`r todays_matches$playerB[ind[2]]`** wins **`r todays_matches$pB[ind[2]] * 100`** % of his first serve points, **`r todays_matches$p2B[ind[2]] * 100`**% of his second serve points, and his first serve in is **`r todays_matches$firstServeB[ind[2]] * 100`**%.

```{r}
match_data <- simMatches(n = 1000,
     pA = todays_matches$pA[ind[2]],
     p2A = todays_matches$p2A[ind[2]],
     firstServeA = todays_matches$firstServeA[ind[2]],
     pB = todays_matches$pB[ind[2]],
     p2B = todays_matches$p2B[ind[2]],
     firstServeB = todays_matches$firstServeB[ind[2]],
     sets = 3,
     players = c(todays_matches$playerA[ind[2]],
                 todays_matches$playerB[ind[2]]))
```

</div>
<div class="col-sm-6">

```{r echo=FALSE}
plot(match_data)

objname <- paste0(c(todays_matches$playerA[ind[2]], todays_matches$playerB[ind[2]]), collapse = "_vs_")
objname <- paste0("data/", gsub(" ", "-", objname), "_", Sys.Date(), ".RDS")
saveRDS(match_data,  objname)
```
</div>
</div>

<hr>

```{r echo=FALSE}
todays_matches[-ind, ] %>%
    select(venue, surface, rd, playerA, pA, p2A, firstServeA, playerB, pB, p2B, firstServeB, winA) %>%
    datatable(rownames = FALSE) %>%
    formatRound(columns = c(5, 6, 7, 9, 10, 11, 12), digits = 2)

```
